Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society

### 2024-09-19 manuscript/appendix.qmd

---
title: >-
  Online appendix for "Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society"
short-title: 'Online appendix for "Enforcing Boundaries"'
date: "2023-12-07"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
bibliography: references.bib
link-citations: true
---

@@

```{r libraries-data}
library(tidyverse)
library(scales)
library(modelsummary)
library(gt)
library(targets)

@@

::: {#tbl-coefs-orig}

\footnotesize

```{r}
#| label: table-coefs-orig
#| include: true

notes <- c(
  "Estimates are median posterior log odds from ordered Beta regression models;",
  "95% credible intervals (highest density posterior interval, or HDPI) in brackets."
)

modelsummary(
  models_tbl$msl, 
  estimate = "{estimate}",
  statistic = "[{conf.low}, {conf.high}]",
  fmt = fmt_significant(2),
  coef_map = models_tbl$nice_coefs,
  output = "gt"
) |> 
  opts_theme() |>
  tab_footnote(
    footnote = paste(notes, collapse = " ")
  ) %>%
  opts_theme() |>
  tab_options(
    quarto.disable_processing = TRUE
  )
```

Complete model coefficients

:::

@@

>>>>

---
title: >-
  Online appendix for "Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society"
short-title: 'Online appendix for "Enforcing Boundaries"'
date: "2023-12-07"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
bibliography: references.json
link-citations: true
---

@@

```{r libraries-data}
library(tidyverse)
library(scales)
library(modelsummary)
library(tinytable)
library(targets)

@@

```{r}
#| label: tbl-coefs-orig
#| tbl-cap: "Complete model coefficients"
#| include: true

notes <- paste(
  "Estimates are median posterior log odds from ordered Beta regression models;",
  "95% credible intervals (highest density posterior interval, or HDPI) in brackets."
)

if (fmt_out == "latex") {
  notes <- str_replace_all(notes, "%", r"(\\%)")
}

inner <- "
row{odd[3-35]}={abovesep=0pt, belowsep=2pt},
row{even[4-36]}={rowsep=0pt},
cells={font=\\footnotesize}, row{1}={valign=b}
"

modelsummary(
  models_tbl$msl,
  estimate = "{estimate}",
  statistic = "[{conf.low}, {conf.high}]",
  fmt = fmt_significant(2),
  coef_map = models_tbl$nice_coefs,
  notes = c(notes),
  width = c(50, 25, 25),
  output = "tinytable"
) |>
  style_tt(j = 2:3, align = "c") |>
  style_tt(i = seq(1, 35, 2), j = 1, rowspan = 2, alignv = "t") |>
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = inner
  )
```

@@

# Comparison of the cases of TNC and Greenpeace

@tbl-case-study summarizes the cases of TNC and Greenpeace. In addition to confirming the correlation between issue area and operational space found in the statistical model, the cases highlight how government preferences exert influence on both the degree of contentious programming INGOs are allowed to undertake and the severity of legal restrictions INGOs can face.

```{r}
#| label: tbl-case-study
#| tbl-cap: "Comparison of the work of The Nature Conservancy and Greenpeace in China"
#| include: true

compare_table <- read_csv(here::here("data", "manual_data", "table-case-study.csv"))

compare_table |>
  rename(` ` = Characteristic) |>
  tt(
    width = c(20, 30, 30)
  ) |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(j = 1:3, align = "l") |>
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = "rowsep=1pt, cells={font=\\footnotesize}"
  )
```

### 2024-09-19 manuscript/manuscript.qmd
Add note from Meng

---
title: "Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society"
short-title: "Enforcing Boundaries"
date: "2024-02-23"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliations: 
    - id: gsu
      name: Georgia State University
      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
      address: "55 Park Place NE, #464"
      city: Atlanta
      region: GA
      country: USA
      postal-code: 30303
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
  attributes:
    corresponding: true
correspondence-prefix: "Correspondence concerning this article should be addressed to"
abstract: |
  China's 2016 Overseas NGO (ONGO) Law is part of a larger global trend of increased legal restrictions on international nongovernmental organizations (INGOs). A growing body of research analyzes the broad effects of this crackdown on INGOs, finding a divergence in formal *de jure* laws and the *de facto* implementation of those laws. The causes and mechanisms of this divergence remain less explored. Why do authoritarian governments allow---and often collaborate---with some INGOs while harshly regulating or expelling others? What determines the openness of the practical legal operating environment for INGOs? In this paper, we use the case of China to explore how political demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the ONGO Law came into effect. We argue that in an effort to bolster regime stability, governments use civil society laws as policy tools to influence INGO behavior. We find that INGO issue areas, missions, and pre-existing relationships with local government officials influence the degree of operating space available for INGOs. We test this argument with a mixed methods research design, combining Bayesian analysis of administrative data from all formally registered INGOs with a comparative case study of two environmental INGOs. Our findings offer insights into the practical effects of INGO restrictions and the dynamics of closing civic space worldwide.
additional-info: |
  **Compliance with Ethical Standards:** This study does not involve human subjects, so the need for participant protection measures such as informed consent, confidentiality, and privacy safeguards was not applicable.

@@

We are not interested in statistical significance or hypothesis testing. Instead, we are interested in the overall registration patterns across our three expectations. Accordingly, while we report full model coefficients, care should be taken to not be concerned if those coefficients are statistically different from zero, or if coefficients for one issue area are statistically different from another issue area. Instead, we use these model results to generate posterior predictions that illustrate the full range of possible registration patterns.

>>>>

---
title: "Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society"
short-title: "Enforcing Boundaries"
date: "2024-09-16"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliations: 
    - id: gsu
      name: Georgia State University
      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
      address: "55 Park Place NE, #464"
      city: Atlanta
      region: GA
      country: USA
      postal-code: 30303
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
  attributes:
    corresponding: true
correspondence-prefix: "Correspondence concerning this article should be addressed to"
abstract: |
  China's 2016 Overseas NGO (ONGO) Law is part of a larger global trend of increased legal restrictions on international nongovernmental organizations (INGOs). A growing body of research analyzes the broad effects of this crackdown on INGOs, finding a divergence in formal *de jure* laws and the *de facto* implementation of those laws. The causes and mechanisms of this divergence remain less explored. Why do authoritarian governments allow---and often collaborate---with some INGOs while harshly regulating or expelling others? What determines the openness of the practical legal operating environment for INGOs? In this paper, we use the case of China to explore how political demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the ONGO Law came into effect. We argue that in an effort to bolster regime stability, governments use civil society laws as policy tools to influence INGO behavior. We find that INGO issue areas, missions, and pre-existing relationships with local government officials influence the degree of operating space available for INGOs. We test this argument with a mixed methods research design, combining Bayesian analysis of administrative data from all formally registered INGOs with a comparative case study of two environmental INGOs. Our findings offer insights into the practical effects of INGO restrictions and the dynamics of closing civic space worldwide.
additional-info: |
  **Compliance with Ethical Standards:** This study does not involve human subjects, so the need for participant protection measures such as informed consent, confidentiality, and privacy safeguards was not applicable.

@@

We are not interested in statistical significance or hypothesis testing. (Meng's note. Starting with the negative sentence may be too blunt. Suggest to change the order of Sentence 1 and Sentence 2). Instead, we are interested in the overall registration patterns across our three expectations. Accordingly, while we report full model coefficients, care should be taken to not be concerned if those coefficients are statistically different from zero, or if coefficients for one issue area are statistically different from another issue area. Instead, we use these model results to generate posterior predictions that illustrate the full range of possible registration patterns.
